\section{StreamSeed Design}
\label{sec:streamseed-design}

StreamSeed targets dynamic ANNS where index quality and workload characteristics co-evolve under continuous updates.
Rather than formulating optimization as an offline pre-processing stage, the design unifies \emph{optimization objectives} and \emph{runtime behavior} within a single online framework: sustaining retrieval quality, preserving throughput stability, and minimizing integration overhead across heterogeneous backends.
This perspective follows directly from the problem analysis in Section 2: hint utility can degrade quickly under updates, trust decisions must be made online at query time, and coarse global refresh is too expensive in high-rate streams.
To address these coupled issues without introducing a monolithic backend-specific solution, StreamSeed organizes the design into two complementary aspects: workload-aligned adaptive reuse and backend-decoupled control.
Accordingly, the design is structured around two core aspects.

\subsection{Design Aspect I: Workload-Aligned Reuse under Drift}
The first aspect is to make reuse \emph{selective and self-correcting} instead of perpetually enabled.
In streaming settings, both data distribution and query focus may evolve rapidly; reuse hints that are beneficial at one time can become counterproductive later.
StreamSeed therefore treats reuse as a provisional hypothesis that must be continuously validated against recent workload evidence.

At a high level, this aspect emphasizes three principles: (1) value-aware reuse only when the expected utility is positive, (2) uncertainty-aware fallback when confidence degrades, and (3) continuous adaptation so that historical signals do not dominate current workload reality.
These principles mitigate quality collapse under drift while preserving acceleration gains in stable phases.
Its implementation is detailed in the first subsection of Section~\ref{sec:implementation}.

\subsection{Design Aspect II: Backend-Decoupled Control Interface}
The second aspect separates optimization policy from index-specific mechanics.
Dynamic ANN systems often incorporate multiple backends with heterogeneous traversal and maintenance behaviors; tightly coupling optimization logic to a single backend reduces portability and increases engineering cost.
StreamSeed therefore defines a lightweight control interface through which the policy layer exchanges only minimal, backend-agnostic signals with the underlying index.

This interface-centric design enables a single policy family to be reused across implementations while preserving backend autonomy for low-level execution.
Consequently, policy and backend optimizations can evolve independently, improving experimental comparability and reducing migration friction in production settings.
Its implementation is detailed in the second subsection of Section~\ref{sec:implementation}.
