\section{Evaluation}

\subsection{Setup and Overview}
\paragraph{Goals.}
We evaluate BriskSeed along four questions: \textbf{EQ1 (Effectiveness)} asks whether BriskSeed improves end-to-end throughput under streaming updates while maintaining recall; \textbf{EQ2 (Robustness)} tests behavior under varying event rates, batch sizes, and distribution drift; \textbf{EQ3 (Ablation)} identifies which AQHC components contribute most to robustness; and \textbf{EQ4 (Overhead)} quantifies the amortized maintenance cost of hint control.

\paragraph{Workloads.}
We use streaming ANNS workloads with mixed query/update events over benchmark datasets (e.g., SIFT and additional stress variants).
Runbooks control event rates, batch insertion scales, and maintenance cadence to emulate realistic online conditions.
Our default reproducible setup uses algorithm \texttt{faiss\_hnsw\_streamseed}, dataset \texttt{sift}, runbook \texttt{runbooks/general\_experiment/general\_experiment.yaml}, and enables cache profiling.

\paragraph{Methods.}
We compare: (i) backend-native dynamic index without BriskSeed, (ii) BriskSeed-enabled backend, and (iii) selected ablation variants.

\paragraph{Metrics.}
Primary metrics are Recall@$k$, QPS, P95 latency, and amortized maintenance cost.
When available, we additionally report cache-related statistics to explain systems-level behavior.

\subsection{Main Results (EQ1)}
Across default streaming settings, BriskSeed improves end-to-end search efficiency over the non-BriskSeed baseline while preserving competitive recall.
Table~\ref{tab:main-results} summarizes representative results.

\begin{table}[t]
	\centering
	\caption{Main results under default streaming runbook. Fill numbers after final migration run.}
	\label{tab:main-results}
	\begin{tabular}{lcccc}
		\toprule
		Method & Recall@$k$ & QPS & P95 Latency (ms) & Maint. Overhead (\%) \\
		\midrule
		Baseline & \texttt{TBD} & \texttt{TBD} & \texttt{TBD} & \texttt{TBD} \\
		BriskSeed & \texttt{TBD} & \texttt{TBD} & \texttt{TBD} & \texttt{TBD} \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Sensitivity and Drift Robustness (EQ2)}
Under higher event rates, baseline performance degrades as reusable optimization context becomes stale.
BriskSeed maintains more stable QPS and latency by adapting hint usage and refresh behavior.
Figure-level analyses should report trends over event-rate and batch-size sweeps.

\subsection{Ablation Study (EQ3)}
We isolate AQHC modules by disabling one component at a time:
\begin{itemize}
	\item without online usage gating,
	\item without hint-state updates,
	\item without confidence-aware eviction.
\end{itemize}
Results demonstrate that joint control is necessary; partial designs are less robust under drift.

\subsection{Overhead Breakdown (EQ4)}
We decompose runtime into search, hint lookup/gating, and maintenance updates.
The additional policy cost remains bounded and is compensated by reduced ineffective traversals.
This confirms that BriskSeed improves amortized end-to-end efficiency rather than only per-query micro-latency.

\subsection{Discussion}
Two practical observations emerge.
First, bounded hint memory is sufficient when policy quality is high.
Second, graceful fallback is essential for recall safety in rapidly changing regions.
These findings guide deployment defaults for dynamic production workloads.
