\section{Problem Statement and Motivation}

\subsection{Problem Statement}
We study dynamic ANNS over a vector collection $\mathcal{D}_t \subset \mathbb{R}^d$ that evolves under a streaming workload.
At each discrete step $t$, the system receives either an update event $u_t \in \mathcal{U}$ (insert/delete) or a query event $q_t \in \mathcal{Q}$.
For each query $q_t$, the index returns an approximate top-$k$ result set $\widehat{N}_k(q_t)$, with quality measured by Recall@$k$:
\begin{equation}
\mathrm{Recall@}k(q_t)=\frac{|\widehat{N}_k(q_t)\cap N_k^{\ast}(q_t)|}{k},
\end{equation}
where $N_k^{\ast}(q_t)$ is the exact top-$k$ neighbor set.

Many fast graph-based systems maintain reusable search artifacts (e.g., entry points, frontier states, local routing hints).
We abstract them as a bounded hint state $\mathcal{H}_t$.
Under a window $W=[t_1,t_2]$, the amortized per-query latency is
\begin{equation}
\bar{L}(W)=\frac{\sum_{q_t\in W} L_{\mathrm{search}}(q_t,\mathcal{H}_t) + \sum_{u_t\in W} L_{\mathrm{maint}}(u_t,\mathcal{H}_t)}{|\{q_t\in W\}|}.
\end{equation}
Our objective is to maximize throughput (equivalently minimize $\bar{L}(W)$) under both quality and memory constraints:
\begin{equation}
\begin{aligned}
\min\ &\bar{L}(W)\\
	ext{s.t. }&\frac{1}{|\{q_t\in W\}|}\sum_{q_t\in W}\mathrm{Recall@}k(q_t)\ge \tau,\\
&|\mathcal{H}_t|\le B,\ \forall t.
\end{aligned}
\end{equation}
Here $\tau$ is the target recall threshold and $B$ is the hint-state budget.

\subsection{Notation Summary}
Table~\ref{tab:notation} summarizes the core symbols used throughout Sections 2--5.
\begin{table}[t]
\caption{Core notation in dynamic ANNS formulation.}
\label{tab:notation}
\centering
\begin{tabular}{ll}
	oprule
Symbol & Meaning \\
\midrule
$\mathcal{D}_t$ & Dynamic vector collection at time $t$ \\
$q_t,\ u_t$ & Query event and update event at time $t$ \\
$\mathcal{H}_t$ & Bounded query-hint state \\
$W=[t_1,t_2]$ & Evaluation window \\
$\bar{L}(W)$ & Amortized per-query latency in $W$ \\
$\tau$ & Target average Recall@$k$ threshold \\
$B$ & Memory budget of hint state \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Motivation from Preliminary Results}
Our preliminary runs on dynamic HNSW show a consistent two-sided failure mode.
When hint maintenance is disabled or too weak, stale hints accumulate and search trajectories drift away from high-quality graph regions, causing rising tail latency and recall loss as update rates increase.
When global maintenance is too aggressive, maintenance overhead dominates amortized latency, offsetting the gain from faster query routing.

This behavior can be summarized as a staleness--overhead tension:
\begin{equation}
\Delta \bar{L} \approx \underbrace{\Delta L_{\mathrm{stale}}}_{\text{insufficient refresh}} + \underbrace{\Delta L_{\mathrm{maint}}}_{\text{excessive refresh}},
\end{equation}
where reducing one term naively often increases the other.
Therefore, dynamic ANNS needs \emph{adaptive} maintenance rather than fixed-period recomputation.

\subsection{Motivational Examples}
	extbf{Example 1: Burst updates.}
In high event-rate intervals, newly inserted vectors quickly change local graph topology.
Hints learned shortly before the burst become unreliable, so blindly reusing them increases traversal detours and cache-miss-heavy random accesses.

	extbf{Example 2: Distribution shift.}
When query focus shifts to a new semantic region, historical hints remain frequent but no longer informative.
Static reuse policies keep activating these high-frequency yet low-value hints, hurting both latency and recall unless the policy can detect and gate them online.

\subsection{Why Existing Approaches Fail in This Regime}
Existing optimizations are mostly designed for static or quasi-static settings, and they break in dynamic streams for three reasons.
First, many methods assume hint validity changes slowly, but stream updates can invalidate local graph neighborhoods within short horizons.
Second, maintenance is often decoupled from online query behavior, so the system cannot decide \emph{when to trust} or \emph{when to fallback} at query time.
Third, global rebuild/reoptimization mechanisms are coarse-grained and cannot match rapidly changing update intensity without either over-paying maintenance cost or under-refreshing hints.

These limitations motivate Section~\ref{sec:streamseed-design}: a unified online control loop that jointly handles hint construction, usage gating, and incremental refresh.
